Irt plot extra

### 2022-09-21 manuscript_v2.Rmd
Comments finalized

  An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours. Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 nationalities, 28 time zones). The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime). In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06). The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega(total)=0.68. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05). Lastly, a short form of the LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).

@@

keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
wordcount         : "X"

@@

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara_dark_2007].

@@

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light? We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations. In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and artificial electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change.

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], a popular measure of sleep quality, contains questions about sleep and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations. To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.

@@

For reliability estimation, the "psych" package was applied [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data[@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.

@@

**Fourthly**, in a secondary analysis, we identified the educational grade level required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package. Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.

@@

In order to improve the model fit, we conducted a post-hoc model modification. Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.  Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ). By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).  Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively.

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**). The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires. The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of 3.33 with age above 8.33 years, implying that the LEBA instrument should be understandable for students of grade four at least 8.33 years old. Furthermore, the
Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarity yielded values between .47 to .51.

@@

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items. The total scale exhibited satisfactory internal consistency (McDonald's $\omega_t$=`r apa(omega$omega.tot,2,T)`).

Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR=`r apa(fit.2[10],2,F) `). In this model, we discarded two additional items (item 26 $\&$ 37 ) for possible cross-loadings. The internal consistency coefficients ordinal alpha for the five factors and the total scale were again satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).

@@

Lastly, we derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@

- In the five factor-solution derived from the Exploratory factor analysis, the internal consistency reliability coefficient ordinal alpha ranged between `r apa(min(alpha.tab),2,F)`-`r apa(max(alpha.tab),2,F)`, though only the fifth factor (“Using light in the morning and during daytime”) yielded internal consistency reliability coefficients below .70 ($\alpha$=`r apa((alpha.tab[5,1]),2,F)`). As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, for scales with less than 20 items and at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Furthermore, the full LEBA scale exhibited satisfactory internal consistency (McDonald’s $\omega_t$=0.77), while all factors were highly interpretable regarding a common behavioural theme. Thus, we decided to proceed with the five-factor solution.
- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit (cf. **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher. We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.

>>>>

  An expert panel prepared the initial 48-item pool spanning different light exposure-related behaviours. Responses, consisting of rating the frequency of engaging in the per-item behaviour on a 5-point Likert type scale, were collected in an online survey yielding responses from a geographically unconstrained sample (690 completed responses, 74 countries, 28 time zones). The exploratory factor analysis (EFA) on an initial subsample (n=428) rendered a five-factor solution with 25 items (Wearing blue light filters, spending time outdoors, using a phone and smartwatch in bed, using light before bedtime, using light in the morning and during daytime). In a confirmatory factor analysis (CFA) performed on an independent subset of participants (n=262), we removed two additional items to attain the best fit for the five-factor solution (CFI=0.95, TLI=0.95, RMSEA=0.06). The internal consistency reliability coefficient for the total instrument yielded McDonald’s Omega=0.68. Measurement model invariance analysis between native and non-native English speakers showed our model attained the highest level of invariance (residual invariance; CFI=0.95, TLI=0.95, RMSEA=0.05). Lastly, a short form of the LEBA (n=18) was developed using Item Response Theory on the complete sample (n=690).

@@

keywords          : "light exposure, light-related behaviours, non-visual effects of light, psychometrics"
wordcount         : "6358"

@@

Light exposure received by the eyes affects many facets of human health, well-being, and performance beyond visual sensation and perception [@boyce_light_2022]. The so-called non-image-forming (NIF) effects of light comprise light’s circadian and non-circadian influence on several physiological and psychological functions, such as the secretion of melatonin, sleep, mood, pupil size, body temperature, alertness, and higher cognitive functions [@Bedrosian.2017;@lok2018light; @siraji2021effects; @blume_effects_2019; @paul_direct_2019; @santhi_applications_2020; @zele_editorial_2020].
With the introduction of artificial electric light, human behaviour has become somewhat independent of the natural light-dark cycle – people can now frequently choose when to be exposed to light or darkness. For example, they can decide whether to go outdoors and seek out sunlight, switch on/off light-emitting devices, use certain types of lights at home, or avoid specific light environments altogether. Additionally, when light sources can not be directly manipulated, sought out, or avoided (for example, at school, work, or in public places), there is still potential leeway to influence them behaviourally, for instance, by wearing sunglasses, directing one’s gaze away or supplementing the situation with additional light sources. Although clearly yielding the potential for good, these behaviours are further associated with increased electric light exposure at night and indoor time during the day, compromising the natural temporal organisation of the light-dark cycle. For example, in the US, an average of 87% of the time is spent in enclosed buildings [@Klepeis.2001], and more than 80% of the population is exposed to a night sky that is brighter than nights with a full moon due to electric light at night [@navara2007dark].

@@

On the other hand, several attempts have been made to quantify received light exposure subjectively with self-report questionnaires (**Supplementary Table 1**), bypassing the cost and intrusiveness issues. However, subjective light intensity assessments pose a new set of challenges: The human visual system constantly adapts to brightness [@hurvich_perception_1966], while the human non-visual light processing works largely subconsciously [@allen_exploiting_2018], making the self-report assessment of light properties potentially quite challenging. Retrospectively recalling the properties of a light source can further complicate such subjective evaluations. Moreover, measuring light properties alone does not yield any information about how individuals might behave differently regarding diverse light environments such  as work, home or outdoors. These measurement limitations point to a couple of research challenges we aim to take on here: How can we gain insight into light exposure patterns via self-report but circumvent directly inquiring about the specific properties and intensity of a light source? And how can we simultaneously assess how people habitually interact with the received light? We propose that these challenges can be tackled by assessing light-exposure-related behaviour. We argue that, besides measuring received light exposure as intensity, it is also essential to understand people's behaviours with respect to different light situations. In many cases, humans have become their own agents regarding their exposure to light or darkness through daylight and electric light, and as such people’s light exposure-related behaviours ultimately determine their light consumption and timing: People receive different light depending on their daily activities, including workplace habits, bedtime hygiene, pastime and social activities. Ultimately, in order to optimize lighting for human health and well being, better understanding of light-related behaviours will serve to identify additional points of intervention as well as to provide an added dimension to efficacy and implementation studies of novel lighting strategies. We argue that assessing these activities is a beneficial stepping stone for prospective behaviour change to maintain light hygiene: a proper balance of exposures to light to maintain circadian rhythms.

To date, little effort has been made to understand and capture these activities. **Supplementary Table 1** summarises the existing questionnaire literature assessing light exposure-related properties. However, only a few questions of these existing tools were associated with light exposure-related behaviour. For example, the “Munich Chronotype  Questionnaire” [@roenneberg2003life], a popular self-report tool for identifying chronotypes via mid-sleep times, includes questions about the individual’s typical time spent outdoors on workdays and free days. The Visual Light Sensitivity Questionnaire-8 [@verriotto2017new] and Photosensitivity Assessment Questionnaire (@bossini2006sensibilita) are a couple of self-report tools measuring visual light sensitivity. They contain single items which probe the preference for specific light situations such as: “In the past month, how often did you need to wear dark glasses on cloudy days or indoors?” [@verriotto2017new];"I prefer rooms that are in semi-darkness."; [@bossini2006sensibilita]. In addition, the “Pittsburgh Sleep Quality Index” [@buysse1989pittsburgh], is a popular measure of sleep quality. It contains questions about bedtime and wake-up times, which are relevant to light exposure around bedtime. However, none of these questionnaires provides a scalable solution to capture light exposure-related behaviour in various lighting situations. To fill this gap, we here present the development process of a novel self-reported tool - the “Light Exposure Behaviour Assessment” (LEBA) - for characterizing diverse light exposure-related behaviours.

@@

For reliability estimation, the "psych" package was applied [@R-psych]. Though Cronbach's internal consistency coefficient alpha is widely used for estimating internal consistency, it tends to deflate the estimates for Likert-type data since the calculation is based on the Pearson-correlation matrix, which requires response data to be continuous in nature [@gadermann2012estimating; @zumbo2007ordinal]. Subsequently, we reported ordinal alpha for each factor obtained in the EFA which was suggested as a better reliability estimates or ordinal data [@zumbo2007ordinal]. We also estimated the internal consistency reliability of the total scale using McDonald's $\omega_t$ coefficient, which was suggested as a better reliability estimate for multidimensional constructs [@dunn2014alpha; @sijtsma2009use]. Both ordinal alpha and McDonald's $\omega_t$ coefficient values range between 0 to 1, where higher values represent better reliability.

@@

**Fourthly**, in a secondary analysis, we identified the educational grade level (US education system) required to understand the items in our scale with the Flesch-Kincaid grade level identification method [@flesch1948new] applying the "koRpus" [@R-koRpus] package. Correspondingly, we analysed possible semantic overlap of our developed scale using the ["Semantic Scale Network" (SSN)](https://rosenbusch.shinyapps.io/semantic_net/) engine [@rosenbusch2020semantic]. The SSN detects semantically related scales and provides a cosine similarity index ranging between -.66 to 1 [@rosenbusch2020semantic]. Pairs of scales with a cosine similarity index value of 1 inidicate full semantical similarity, suggesting redundancy.

@@

In order to improve the model fit, we conducted a post-hoc model modification. Firstly, the  modification indices suggested cross-loadings between item 37 and 26 [item 37: I purposely leave a light on in my sleep environment while sleeping; item 26: I turn on my ceiling room light when it is light outside], which were hence discarded.  Secondly, items 30 and 41 [item 30: I look at my smartwatch within 1 hour before attempting to fall asleep; item 41: I look at my smartwatch when I wake up at night] showed a tendency to co-vary in their error variance (MI = 141.127, p<.001 ). By allowing the latter pair of items (30 $\&$ 41) to co-vary, the model's error variance attained an improved fit (CFI =`r apa(fit.2[5],2,F)`; TLI = `r apa(fit.2[6],2,F)`); RMSEA = `r apa(fit.2[7],2,F)` [`r apa(fit.2[8],2,F)`-`r apa(fit.2[9],2,F)`, 90% CI]; SRMR = `r apa(fit.2[10],2,F) `).

Accordingly, we accept the five-factor model with 23 items, finalizing the long Form of LEBA (see **Supplementary File 1**). Internal consistency ordinal $\alpha$ for the five factors of the LEBA were `r apa(rel.k[2,1],2,F)`, `r apa(rel.k[2,2],2,F)`, `r apa(rel.k[2,3],2,F)`, `r apa(rel.k[2,4],2,F)`, `r apa(rel.k[2,5],2,F)`, respectively. The Internal consistency McDonald's $\omega_t$ coefficient for the total scale yielded `r apa(rel.k[5,6],2,F)`. Figure \@ref(fig:figcfa) depicts the obtained CFA structure, while  **Supplementary Figure 2** depicts the data distribution and endorsement pattern of the retained 23 items in our CFA sample.

@@

## Secondary Analysis: Grade Level Identification and Semantic Scale Network Analysis
A grade level identification and Semantic Scale analysis were additionally administered to assess the LEBA's (23 items) language-based accessibility and its' semantic relation to other questionnaires. The results of the Flesch-Kincaid grade level analysis [@flesch1948new] displayed a required educational grade level of four (US education system) with age above 8.33 years. Furthermore, the
Semantic Scale Network (SSN) analysis [@rosenbusch2020semantic] indicated that the LEBA appeared most strongly semantically related to scales about sleep: The "Sleep Disturbance Scale For Children" [@bruni1996sleep] and the "Composite International Diagnostic Interview (CIDI): Insomnia"[@robins1988composite]. The cosine similarity yielded values between .47 to .51.

@@

Data collected in the first round was used to explore the latent structure (EFA sample; n=`r nrow(EFA.descriptives)`). The exploratory factor analysis revealed a highly interpretable five-factor solution ("Wearing blue light filters", "Spending time outdoors", "Using phone and smartwatch in bed", "Using light before bedtime", and "Using light in the morning and during daytime") with 25 items. Our CFA analysis (CFA sample; n=`r nrow(CFA.descriptives)`) confirmed the five-factor structure we obtained in our EFA, thus providing evidence for structural validity.(CFI=`r apa(fit.2[5],2,F)`; TLI=`r apa(fit.2[6],2,F)`; RMSEA=`r apa(fit.2[7],2,F)`). In this model, we discarded two more items (item 26 $\&$ 37 ) for possible cross-loadings. As a rule of thumb, reliability coefficients higher than .70 are regarded as “satisfactory”. However, at the early developmental stage, a value of .50 is considered acceptable [@dall2010developmental; @field2013discovering; @Nunnally1978]. Thus, we confer, the internal consistency coefficients ordinal alpha for the five factors and the total scale were satisfactory (Ordinal alpha ranged between `r apa(min(rel.k[2,(1:5)]),2,T)` to `r apa(max(rel.k[2,(1:5)]),2,T)`; McDonald's $\omega_t$=`r apa(rel.k[5,6],2,F)`).

@@

Often psychological measurements require application of several questionnaires simultaneously. Responding to several lengthy questionnaires increases the participants losing focus and becoming tried. To avoid these situations we  derived a short version of the LEBA (18 items) using IRT analysis. We fitted a graded response model to the combined EFA and CFA sample (n=`r nrow(data)`) and discarded five items (1, 25, 30, 38, & 41) with relatively flat item information curve [I($\theta$) <.20]. The resulting test information curves suggest that the short-LEBA is a psychometrically sound measure with adequate coverage of underlying traits and can be applied to capture the frequency of different light exposure related behaviours reliably.

@@

- The fifth factor: "using light in the morning and during daytime" exhibited low internal consistency both in the exploratory and confirmatory factor analysis (EFA: `r apa(F5.alpha,2,F)`; CFA:`r apa(rel.k[2,5],2,F)` ). Since, it was above .50, considering the developmental phase of this scale we accepted the fifth factor. 
- During the post-hoc model modification, as part of the confirmatory factor analysis, we discarded two items (item 26 $\&$ 37 ) for possible cross-loadings, as demonstrated in the data. However, two additional items covaried in their error variance. By allowing the latter pair (30 $\&$ 41) to covary, the model attained an improved fit ( **Figure 5**). A possible explanation for the covariation is that many respondents might not have used a smartwatch at all, resulting in similar response patterns between these two items. Thus, though rather unconventional, we decided to accept this post-hoc modification to our five-factor model.
- The habitual patterns queried in the developed scales might not exhaustively represent all relevant light-exposure-related behaviours. For instance, it is conceivable that additional light-related activities not included in the LEBA depend on the respondents' profession/occupation, geographical context, and socio-economic status. However, we generated the initial item pool with an international team of researchers and followed a thorough psychometric analysis. Therefore, we are confident that the developed LEBA scales can serve as a good starting point for exploring the light exposure related behaviours in more depth and inform room for modification of light exposure-related behaviour to improve light hygiene.
- As with all studies relying on retrospective self-report data, individuals filling in the LEBA may have difficulties precisely recalling the inquired light-related behaviours. In the interest of bypassing a substantial memory component, we limited the recall period to four weeks and chose response options that do not require exact memory recall. In contrast to directly assessing light properties via self-report, we assume that reporting behaviours might be more manageable for inexperienced laypeople, as the latter does not rely on existing knowledge about light sources. The accessibility of the LEBA is also reflected in the “grade level identification” findings suggesting a minimum age of 8.33 years and an educational grade of four or higher. We argue that measuring light-related behaviours via self-report is crucial because these behaviours will hardly be as observable by anyone else or measurable with other methods (like behavioural observations) with reasonable effort.
